---
title: "Anova_for_genome size"
output: html_document
---

# Upload Library
```{r}
library(dplyr)
library(multcompView)
```

# Loading file 
```{r}
Data <- read.csv("review_work.csv")
Data
```

# Calculating of mean and standard deviation.
```{r}
Data_mean_SD <-group_by(Data, Species) %>% summarise(count = n(),mean = mean(Genome_Size, na.rm = TRUE),sd = sd(Genome_Size, na.rm = TRUE))

Data_mean_SD
```

# Anova analysis

We are using one-way ANOVA to find out if there is a difference in genome sizes between the different species.

```{r}
res.aov <- aov(Genome_Size ~ Species, data = Data)
summary(res.aov)
```

The p value of <2e-16 was the one I wrote in the manuscript.

# There was a significant difference in genome sizes [F(5,42)= 597, p <2e-16 ] between the species.

Now lets see which species are different using Post-hoc test.

# Tukey post host test

```{r}
tukey <- TukeyHSD(res.aov)
tukey
```

We can see which groups are different based on p value. Let's assign letter to make it easier to see different groups.

# Creating compact letter display using multcompView
```{r}
tukey.cld <- multcompLetters4(res.aov, tukey)
print(tukey.cld)
```
